---
title: "Transform Data"
output:
  html_document:
    df_print: paged
---

```{r setup}
# If you need to install these packages:
# install.packages(c("tidyverse", "gapminder"))

library(tidyverse)
library(gapminder)
diabetes <- read_csv("diabetes.csv")
```

## Your Turn 1

Here is a list:

```{r}
number_list <- list(
  a = rnorm(100, mean = 2, sd = 1.4), 
  b = rnorm(100, mean = 1, sd = 1), 
  c = rnorm(100, mean = 10, sd = 3)
)

number_list
```

There are two ways to subset lists: dollar signs and brackets. Try to subset `a` from `number_list` using these approaches. Are they different? What about `number_list[["a"]]`?

```{r}
number_list["a"]
```

```{r}
number_list$a
```

## Your Turn 2

What will each of these return? Run the code chunks to confirm.

```{r}
vec <- c(-2, -1, 0, 1, 2)
sum(vec)
```

```{r}
sum(number_list)
```

## Your Turn 3

Run the code in the chunks. What does it return?

```{r}
list(
  sum_a = sum(number_list$a),
  sum_b = sum(number_list$b),
  sum_c = sum(number_list$c)
)
```

```{r}
map(number_list, sum)
```

## Your Turn 4

Pass diabetes to `map()` and map using `class()`. What are these results telling you?

```{r}
map(diabetes, class)
```


## Your Turn 5

Write a function that returns the mean and standard deviation of a numeric vector.
1. Give the function a name
2. Find the mean and SD of `x`
3. Map your function to `number_list`

```{r}
mean_sd <- function(x) {
  x_mean <- mean(x)
  x_sd <- sd(x)
  c(mean = x_mean, sd = x_sd)
}
  
map(number_list, mean_sd)
```

## Your Turn 6

Do the same as #4 above but return a vector. Try writing your function as an anonymous function or using the ~.f(.x) shorthand.

```{r}
map_chr(diabetes, class)
map_chr(diabetes, function(.x) class(.x))
map_chr(diabetes, ~class(.x))
```


## Your Turn 7

Check `diabetes` for any missing data. 

1. Using the ~.f(.x) shorthand, check each column for any missing values using `is.na()` and `any()`
2. Return a logical vector. Are any columns missing data? What happens if you don't include `any()`? Why?
3. Try counting the number of missing, returning an integer vector

```{r}
map_lgl(diabetes, ~any(is.na(.x)))
map_int(diabetes, ~sum(is.na(.x)))
```

## Your Turn 8

1. Turn `diabetes` into a list split by `location` using the `split()` function. Check its length.
2. Fill in the `model_lm` function to model `chol` (the outcome) with `ratio` and pass the `.data` argument to `lm()`
3. map `model_lm` to `diabetes_list` so that it returns a data frame (by row).

```{r}
diabetes_list <- split(diabetes, diabetes$location)
length(diabetes_list)
model_lm <- function(.data) {
  mdl <- lm(chol ~ ratio, data = .data)
  # get model statistics
  broom::glance(mdl)
}

map_dfr(diabetes_list, model_lm)
```

## Your Turn 9

1. Pass both `means` and `sds` to `rnorm()` to return a random variable for each pair. Return a numeric vector.

```{r}
means <- c(-3, 4, 2, 2.3)
sds <- c(.3, 4, 2, 1)
  
map2_dbl(means, sds, rnorm, n = 1)
```

## Your Turn 10

Do the same as #8, but use a nested data frame.
1. Create a nested data frame. What does it look like?
2. Use `map()` in `dplyr::mutate()` to map `data` to `model_lm`. 
3. What does `nested_glance` look like?
4. Unnest the data. In what ways does it look different than #8?

```{r}
diabetes_nested <- diabetes %>% 
  group_by(location) %>% 
  nest()

nested_glance <- diabetes_nested %>% 
  mutate(glance = map(data, model_lm))

nested_glance
  
unnest(nested_glance, glance)
```
